### 2025-07-19 decision-making.qmd
20250708 - track chunk execution times
20250717 - chapter overviews
20250719 - bracketing rate

@@

@@

- <https://www.rotowire.com/betting/nfl/player-futures.php>
- <https://vegasprojections.com>
- <https://www.actionnetwork.com/nfl/props>

@@

```{r}
# insert example using historical projections: wisdomOfCrowd()
```

>>>>

This chapter provides an overview of various considerations in judgment and decision making in the context of uncertainty.

@@

### Load Data {#sec-decisionMakingLoadData}

```{r}
#| eval: false
#| include: false

load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/projectionsWithActuals_seasonal.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/projectionsWithActuals_weekly.RData", fsep = ""))
#load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/players_projections_seasonal.RData", fsep = ""))
#load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/players_projections_weekly.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/player_stats_seasonal.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/player_stats_weekly.RData", fsep = ""))
```

```{r}
load(file = "./data/projectionsWithActuals_seasonal.RData")
load(file = "./data/projectionsWithActuals_weekly.RData")
#load(file = "./data/players_projections_seasonal.RData")
#load(file = "./data/players_projections_weekly.RData")
load(file = "./data/player_stats_seasonal.RData")
load(file = "./data/player_stats_weekly.RData")
```

We created the `projectionsWithActuals_seasonal.RData` object in @sec-predictionAccuracyPrepareDataSeasonal; we created the `projectionsWithActuals_weekly.RData` object in @sec-predictionAccuracyPrepareDataWeekly.

@@

- <https://www.rotowire.com/betting/nfl/player-futures.php>
- <https://vegasprojections.com>
- <https://www.actionnetwork.com/nfl/props>
- <https://tools.32beatwriters.com>
- <https://the-odds-api.com>

@@

### Seasonal Projections {#sec-accuracyOfCrowdSeasonal}

```{r}
# insert example using historical projections: wisdomOfCrowd()

seasonalIndividualSources <- projectionsWithActuals_seasonal %>%
  filter(!is.na(raw_points)) %>% 
  filter(!is.na(fantasyPoints)) %>% 
  group_by(player_id, season) %>%
  filter(n() >= 2) %>% # at least 2 projections
  summarise(
    numProjections = n(),
    type = "individual",
    petersenlab::wisdomOfCrowd(
      predicted = raw_points,
      actual = unique(fantasyPoints),
      dropUndefined = TRUE
      )[1,],
    .groups = "drop"
  )

seasonalCrowd <- projectionsWithActuals_seasonal %>%
  filter(!is.na(raw_points)) %>% 
  filter(!is.na(fantasyPoints)) %>% 
  group_by(player_id, season) %>%
  filter(n() >= 2) %>% # at least 2 projections
  summarise(
    numProjections = n(),
    type = "crowd",
    petersenlab::wisdomOfCrowd(
      predicted = raw_points,
      actual = unique(fantasyPoints),
      dropUndefined = TRUE
      )[2,],
    .groups = "drop"
  )

seasonalIndividualSourcesAndCrowd <- bind_rows(
  seasonalIndividualSources,
  seasonalCrowd
)

seasonalIndividualSources <- seasonalIndividualSources %>% 
  left_join(
    player_stats_seasonal,
    by = c("player_id", "season")
  )

seasonalCrowd <- seasonalCrowd %>% 
  left_join(
    player_stats_seasonal,
    by = c("player_id", "season")
  )

seasonalIndividualSourcesAndCrowd <- seasonalIndividualSourcesAndCrowd %>% 
  left_join(
    player_stats_seasonal,
    by = c("player_id", "season")
  )
```

```{r}
#| label: fig-bracketingRateSeasonal
#| fig-cap: "Distribution of Bracketing Rate Across Players For Seasonal Projections."
#| fig-alt: "Distribution of Bracketing Rate Across Players For Seasonal Projections."

ggplot2::ggplot(
  data = seasonalIndividualSources %>%
    filter(position_group %in% c("QB","RB","WR","TE")),
  mapping = aes(
    x = bracketingRate)
) +
  geom_histogram(
    color = "#000000",
    fill = "#0099F8"
  ) +
  labs(
    x = "Bracketing Rate",
    y = "Count",
    title = "Histogram of Bracketing Rate (Seasonal Projections)"
  ) +
  theme_classic() +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5))
```

Proportion of players whose bracketing rate was zero:

```{r}
#length()
```

### Weekly Projections {#sec-accuracyOfCrowdWeekly}

### Examples {#sec-accuracyOfCrowdExamples}

### 2025-07-19 evaluating-prediction-accuracy.qmd
20250719 - bracketing rate

players_projectedPoints_seasonal_combined$season <- as.integer(players_projectedPoints_seasonal_combined$season)

@@

@@

playersWithHighProjectedOrActualPoints <- projectionsWithActuals_seasonal %>% 
  filter(raw_points > 100 | fantasyPoints > 100) %>% 
  select(player_id_season) %>% 
  pull()

@@

Players are uniquely identified by `player_id`-`season`-`data_src`:

@@

players_projectedPoints_weekly_combined$season <- as.integer(players_projectedPoints_weekly_combined$season)

@@

@@

playersWithHighProjectedOrActualPoints_weekly <- projectionsWithActuals_weekly %>% 
  filter(raw_points > 6 | fantasyPoints > 6) %>% 
  select(player_id_season_week) %>% 
  pull()

@@

Players are uniquely identified by `player_id`-`season`-`week`-`data_src`:

@@

Here are the weekly accuracy indexes for players across all positions, but only among those who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

Here are the weekly accuracy indexes for only those Quarterbacks who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

Here are the weekly accuracy indexes for only those Running Backs who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

Here are the weekly accuracy indexes for only those Wide Receivers who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

Here are the weekly accuracy indexes for only those Tight Ends who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

Here are the weekly accuracy indexes for only those Kickers who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

Here are the weekly accuracy indexes for only those Defensive Linemen who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

Here are the weekly accuracy indexes for only those Linebackers who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

Here are the weekly accuracy indexes for only those Defensive Backs who had high projected or actual points (i.e., players who had more than 100 projected or actual points; the players that are most important to differentiate between):

@@

```{r}
#| label: tbl-weeklyAccuracyByPositionSubset
#| tbl-cap: "Accuracy of Weekly Projections By Position, Among Players with Greater than 100 Projected or Actual Points."
#| echo: false

>>>>

players_projectedPoints_seasonal_combined$season <- as.integer(players_projectedPoints_seasonal_combined$season)
players_projections_seasonal_average_merged$season <- as.integer(players_projections_seasonal_average_merged$season)

@@

crowdAveragedProjectionsWithActuals_seasonal <- full_join(
  player_stats_seasonal_subset_IDs,
  players_projections_seasonal_average_merged %>% filter(avg_type == "average"),
  by = c("mfl_id" = "id", "season"),
  suffix = c("", "_proj"),
)

@@

crowdAveragedProjectionsWithActuals_seasonal <- crowdAveragedProjectionsWithActuals_seasonal %>% 
  unite(
    "player_id_season",
    player_id,
    season,
    remove = FALSE
  )
```

Players in the `projectionsWithActuals_seasonal` object are (supposed to be) uniquely identified by `player_id`-`season`-`data_src`:

Players in the `crowdAveragedProjectionsWithActuals_seasonal` object are (supposed to be) uniquely identified by `player_id`-`season`-`avg_type`:

```{r}
crowdAveragedProjectionsWithActuals_seasonal %>% 
  filter(!is.na(player_id)) %>% 
  group_by(player_id, season, avg_type) %>% 
  filter(n() > 1) %>% 
  head()
```

We save the data object for use in other chapters:

```{r}
save(
  projectionsWithActuals_seasonal, crowdAveragedProjectionsWithActuals_seasonal,
  file = "./data/projectionsWithActuals_seasonal.RData"
)
```

```{r}
playersWithHighProjectedOrActualPoints <- projectionsWithActuals_seasonal %>% 
  filter(raw_points > 100 | fantasyPoints > 100) %>% 
  select(player_id_season) %>% 
  pull()

@@

@@

players_projectedPoints_weekly_combined$season <- as.integer(players_projectedPoints_weekly_combined$season)
players_projections_weekly_average_merged$season <- as.integer(players_projections_weekly_average_merged$season)

@@

crowdAveragedProjectionsWithActuals_weekly <- full_join(
  player_stats_weekly_subset_IDs,
  players_projections_weekly_average_merged,
  by = c("mfl_id" = "id", "season", "week"),
  suffix = c("", "_proj"),
)

@@

crowdAveragedProjectionsWithActuals_weekly <- crowdAveragedProjectionsWithActuals_weekly %>% 
  unite(
    "player_id_season_week",
    player_id,
    season,
    week,
    remove = FALSE
  )
```

Players in the `projectionsWithActuals_weekly` object are (supposed to be) uniquely identified by `player_id`-`season`-`week`-`data_src`:

Players in the `crowdAveragedProjectionsWithActuals_weekly` object are (supposed to be) uniquely identified by `player_id`-`season`-`week`-`avg_type`:

```{r}
crowdAveragedProjectionsWithActuals_weekly %>% 
  filter(!is.na(player_id)) %>% 
  group_by(player_id, season, week, avg_type) %>% 
  filter(n() > 1) %>% 
  head()
```

We save the data object for use in other chapters:

```{r}
save(
  projectionsWithActuals_weekly, crowdAveragedProjectionsWithActuals_weekly,
  file = "./data/projectionsWithActuals_weekly.RData"
)
```

```{r}
playersWithHighProjectedOrActualPoints_weekly <- projectionsWithActuals_weekly %>% 
  filter(raw_points > 6 | fantasyPoints > 6) %>% 
  select(player_id_season_week) %>% 
  pull()

@@

@@

Here are the weekly accuracy indexes for players across all positions, but only among those who had high projected or actual points (i.e., players who had more than 6 projected or actual points; the players that are most important to differentiate between):

@@

Here are the weekly accuracy indexes for only those Quarterbacks who had high projected or actual points (i.e., players who had more than 6 projected or actual points; the players that are most important to differentiate between):

@@

Here are the weekly accuracy indexes for only those Running Backs who had high projected or actual points (i.e., players who had more than 6 projected or actual points; the players that are most important to differentiate between):

@@

Here are the weekly accuracy indexes for only those Wide Receivers who had high projected or actual points (i.e., players who had more than 6 projected or actual points; the players that are most important to differentiate between):

@@

Here are the weekly accuracy indexes for only those Tight Ends who had high projected or actual points (i.e., players who had more than 6 projected or actual points; the players that are most important to differentiate between):

@@

Here are the weekly accuracy indexes for only those Kickers who had high projected or actual points (i.e., players who had more than 6 projected or actual points; the players that are most important to differentiate between):

@@

Here are the weekly accuracy indexes for only those Defensive Linemen who had high projected or actual points (i.e., players who had more than 6 projected or actual points; the players that are most important to differentiate between):

@@

Here are the weekly accuracy indexes for only those Linebackers who had high projected or actual points (i.e., players who had more than 6 projected or actual points; the players that are most important to differentiate between):

@@

Here are the weekly accuracy indexes for only those Defensive Backs who had high projected or actual points (i.e., players who had more than 6 projected or actual points; the players that are most important to differentiate between):

@@

```{r}
#| label: tbl-weeklyAccuracyByPositionSubset
#| tbl-cap: "Accuracy of Weekly Projections By Position, Among Players with Greater than 6 Projected or Actual Points."
#| echo: false
